News Topic Modeling

### 2017-12-08 paper/R/03_stm.Rmd
new

```{r Setup}
suppressPackageStartupMessages({
  library(dplyr)       # Data manipulation
  library(stringr)     # String manipulation
  library(lubridate)   # Date and time manipulation
  library(purrr)       # Functional programming
  library(tidyr)       # Reshaping
  library(magrittr)    # Advanced piping
  library(pushoverr)   # Pushover notifications
  library(doMC)        # Parallel Computing
  library(readr)       # Importing data
  library(tibble)      # Better data frames
  library(data.table)

@@

rm(list=ls())
# Functions
source("func/02-topic-modelling-functions.R")
```

```{r caching, echo=, message=FALSE, warning=FALSE}
load("../output/btw_combined.Rda")

#load("../output/models/STM 50 .Rda")
knitr::opts_chunk$set(eval = TRUE, warning = FALSE, message = FALSE)
```

## Explore Dataset
```{r}
library(RColorBrewer) 
col <- brewer.pal(7,"Dark2")
```

```{r message=FALSE, warning=FALSE}
btw %>%
  group_by(date, site) %>%
  summarise(obs = n()) %>%
  ggplot(aes(date, obs, color = site)) +
  geom_line() +
  scale_color_manual(values = col) +
  theme(legend.position="none") +
  labs(x="", y="Count",color="") +
  scale_x_date(breaks = date_breaks("2 weeks"), labels=date_format("%d.%m", tz="CET"))

# ggsave("../figs/timeline.png", plot = last_plot(), device = "png", 
#        dpi = 600)
```

```{r message=FALSE, warning=FALSE}
btw %>%
  ggplot(aes(site)) +
  geom_bar(fill=col, alpha= .8) +
  labs(x="", y="Count")

# ggsave("../figs/bar.png", plot = last_plot(), device = "png", 
#        dpi = 600)
```

```{r message=FALSE, warning=FALSE}
btw %>%
  ggplot(aes(date, site, size=text_length, color = site)) +
  geom_point(show.legend = FALSE, alpha = .8) +
  scale_color_manual(values = col) +
  labs(x="", y="")

# ggsave("../figs/fb_shares.png", plot = last_plot(), device = "png", 
#        dpi = 600)
```

```{r message=FALSE, warning=FALSE}
btw %>%
  ggplot(aes(site, text_length)) +
  stat_summary(fun.y="median", geom="bar", fill = col, alpha = .8) +
  labs(x="", y="")

#ggsave("../figs/fb_shares_mean.png", plot = last_plot(), 
#       dpi = 600)
```

# Structural Topic Model
## Build Corpus
```{r eval=FALSE, include=FALSE}
# Process data
processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("site","text_cleaned","month")],
                           wordLengths = c(2,Inf),
                           lowercase = F,
                           removestopwords = F,
                           removenumbers = F,
                           removepunctuation = F,
                           stem = F)
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
```

### Select number of topics
```{r}
K<-c(30,40,50,60,80)

t1 <- Sys.time()
kresult <- searchK(out$documents, out$vocab, K, prevalence=~site + s(btw_dummy), data = out$meta, init.type = "Spectral")
t2 <- Sys.time()
t2 - t1

save(btw, out, kresult, file="../output/models/kresult.Rda")
#load(file="../output/models/kresult.Rda")
```

@@

We then train the Structural Topic Model on the full dataset, with $k = 50$.

```{r}
k = 40 # Topics

@@

save(stmOut, btw, out, file=paste("../output/models/STM",k,".Rda"))

#load(file=paste("../output/models/STM",k,".Rda"))
```

@@

### Using build-in functions
#### Topic Summary
```{r}
plot(stmOut, type = "summary", xlim = c(0,.14), n = 5, #labeltype = "frex",
         main = "Online News Topics", text.cex = 0.8)
```

The most frequent words in the model such as for topics #3, #7, and #20
```{r}
plot(stmOut, type="labels", topics=c(37,8))
```

A comparison of two topics 
```{r}
plot(stmOut, type="perspectives", topics=c(37,8))
```

The estimateEffect() function explores how prevalence of topics varies across documents according to document covariates (metadata). First, users must specify the variable that they wish to use for calculating an effect. If there are multiple variables specified in estimateEffect(), then all other variables are held at their sample median. These parameters include the expected proportion of a document that belongs to a topic as a function of a covariate, or a first difference type estimate, where topic prevalence for a particular topic is contrasted for two groups
```{r}
out$meta$site <- as.factor(out$meta$site)
prep <- estimateEffect(1:50 ~ site+s(month), stmOut, meta=out$meta, uncertainty = "Global")
```

To see how prevalence of topics differs across values of a continuous covariate:
```{r}
plot(prep, "month", method="continuous", topics = c(46,42),
     xlab="Month (2017)")
monthseq <- seq(from=as.Date("2017-06-01"), to=as.Date("2017-11-01"), by="month")
monthnames <- month(monthseq)
axis(1, at=as.numeric(monthseq), labels = monthnames)
```

#### Topic Labeling
```{r Tokenize}
btw %>% 
  # Tokenize by word
  unnest_tokens(word, text_cleaned, token = "words") %>%
  # Remove short words
  filter(str_length(word) >= 3) ->
  # Assign to variable
  posts_tokenized.dt

```{r Extract wtp and dtp}
# Word-topic probabilities
stmOut %>% tidy("beta") %>% filter(!is.na(topic)) -> posts.wtp

@@

To get an idea of the topics, we take a look at the words that are associated with topics and label them accordingly. We then inspect the documents that are estimated to be highly associated with each topic. Figure --- shows a random sample of 7 posts from the 300 highest probability fits per topic.

```{r Compute relevance}
posts.wtp %>%
    filter(str_length(term) >= 3) %>%
  # Compute lambda and phi_kw
  mutate(lambda = 0.6, phi_kw = beta) %>% 
  # Compute and join the p_w
  left_join(
    posts_tokenized.dt %>%
      group_by(word) %>% 
      dplyr::summarise(frequency = sum(term_frequency)) %>% 
      ungroup() %>% 
      mutate(p_w = frequency/sum(frequency)) %>% 
      select(-frequency),
    by = c("term" = "word")
  ) %>%
  # Compute the relevance
  mutate(relevance = lambda * log(phi_kw) + (1 - lambda) * log(phi_kw/p_w)) ->
  word_relevance.dt

```{r Label Topics}
label <- labelTopics(stmOut, n=4)

topicLabel <- as.data.frame(label$prob)
topicLabel <- topicLabel %>%
  transmute(topic = rownames(.),
    topic_name = paste(V1,V2,V3,V4, sep = ", "))

frex <- as.data.frame(label$frex)
topicLabel <- topicLabel %>%
  left_join(., 
            frex %>%
              transmute(topic = rownames(.),
                frex = paste(V1,V2,V3,V4, sep=", ")),
            by = "topic")

lift <- as.data.frame(label$lift)
topicLabel <- topicLabel %>%
  left_join(., 
            lift %>%
              transmute(topic = rownames(.),
                lift = paste(V1,V2,V3,V4, sep=", ")),
            by = "topic")

score <- as.data.frame(label$score)
topicLabel <- topicLabel %>%
  left_join(., 
            score %>%
              transmute(topic = rownames(.),
                score = paste(V1,V2,V3,V4, sep=", ")),
            by = "topic")

rm(frex, lift, score)
```

```{r Add Topic to original DF}
# Create Dataframe
theta <- as.data.frame(stmOut$theta)
theta$topic <- colnames(theta)[apply(theta,1,which.max)]

doctopics.df <- theta %>%
  transmute(articleID = as.numeric(rownames(.)),
    topic = as.numeric(gsub("V","",topic)))

# Add Topic to origian DF
btw %>%
  inner_join(.,doctopics.df, by="articleID") %>%
  ## Combine with Topic label
  left_join(., topicLabel %>%
              select(topic_name, topic) %>%
              mutate(topic = as.numeric(topic)), by="topic") -> btw

@@

To test, wheather the topic classification make sense, we pull out sample articles classified by the model to see if they match the assigned topic.

@@

posts_classification.sdt <-
  posts.dtp %>% 
  group_by(articleID = document) %>% 
  summarise(topic = min(topic[gamma == max(gamma)]), gamma = max(gamma)) %>% 
  ungroup() %>%
  inner_join(btw %>% select(title, title_text, articleID, topic_name),
              by = "articleID") %>%
  #inner_join(topics_mapping.dt, by = "topic") %>%
  mutate(topic_title = 
           paste0("Topic ", formatC(topic, flag = "0", width = 2), 
                  " - ", topic_name)) %>%
  group_by(topic_name) %>% 
  top_n(300, gamma) %>%
  sample_n(7) %>% 
  mutate(row = row_number()) %>% 
  ungroup()

@@

ggsave(
  plot = {
    posts_classification.sdt %>% 
      ggplot(aes(x = 0, y = row, color = factor(topic, levels = 1:40))) +
      facet_wrap(~topic_title, ncol = 5) +
      geom_text(
        aes(label = title),
        size = 2, hjust = 0, family = "Roboto"
      ) +
      geom_point(aes(x = -0.025), size = 0.5) +
      scale_x_continuous(limits = c(-0.05, 1), expand = c(0, 0)) +
      scale_color_manual(
        values = rainbow(50) %>% 
          adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
      ) +
      theme(
        axis.title       = element_blank(),
        axis.text        = element_blank(),
        axis.ticks       = element_blank(),
        panel.grid       = element_blank(),
        strip.background = element_blank(),
        panel.border     = element_blank(),
        strip.text       = element_text(face = "bold", hjust = 0, size = 6),
        plot.background  = element_rect(fill = "#FAFAFA"),
        legend.position  = "none"
      ) 
  },
  device = "png",
  filename = "../figs/topic-classification-sample.png",
  dpi = 600, height = 10, width = 16
)

@@

![Facebook news samples](../figs/02-topic-classification-sample.png)
### News landscape

@@

    ggsave(
      plot = {
        topic_labelling_top30words.dt %>% 
          ggplot(aes(x = x, y = y)) +
          geom_text_repel(
            aes(label = term, 
                color = factor(topic, levels = 1:40), 
                size = phi_kw * p_w), 
            lineheight = 0.6, 
            segment.size = NA,
            box.padding = unit(0, "lines"),
            force = 0.05,
            family = "Roboto"
          ) +
          geom_text_repel(
            data = topic_labelling_topics.dt,
            aes(label = str_wrap(topic_name, 15),
                color = factor(topic, levels = 1:40)),
            size = 2.25, lineheight = 0.7,
            segment.size = 0.5, alpha = 0.7,
            family = "Roboto", fontface = 2,
            force = 0.3
          ) +
          scale_size_continuous(range = c(1, 4)) +
          scale_color_manual(
            values = rainbow(39) %>% 
              adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
          ) +
          theme(
            axis.title = element_blank(),
            axis.text  = element_blank(),
            axis.ticks = element_blank(),
            panel.grid = element_blank(),
            panel.border = element_blank(),
            plot.background = element_rect(fill = "#FAFAFA"),
            legend.position = "none"
          ) +
          labs(
            title    = ""
          )
      },
      filename = "../figs/news-landscape-map.png",
      device = "png",
      dpi = 600
    )

@@

![Facebook News Map](../figs/news-landscape-map.png)

```{r}
btw %>%
  #filter(topic==4) %>%
  filter(startsWith(title,"News")) %>%
  select(url,title, text)
```

@@

## Regression

### Facebook Shares
```{r Facebook Shares}
btw2 %>%
  ggplot(aes(as.factor(topic), fb_shares)) +
  stat_summary(fun.y="sum", geom="bar", fill = "blue", alpha=.7) +
  labs(x="", y="Sum") +
  scale_x_discrete(breaks=c(1:50), labels = topicLabel$topic_name) +
  theme(axis.text.x = element_text(size=7, angle=90),
        axis.text.y = element_text(size=7))

ggsave("../figs/fb_shares_topics.png", device = "png", 
       dpi = 600)
```

### Prepare Data
```{r}
top_topics <-
  posts.dtp %>% 
  group_by(document) %>%
  mutate(therank = rank(-gamma, ties.method = "random")) %>%
  filter(therank %in% 1) %>%
  select(- therank)
```

```{r}
# filter documents with low posterior
btw.reg <- 
  btw %>%
  mutate(document = as.numeric(articleID)) %>%
  left_join(., top_topics, by="document") %>%
  #filter(gamma > 0.6) %>%
  filter(fb_shares > 0)

# generate factor variables
btw.reg %>%
  mutate(topic.f = factor(topic),
         site.f = factor(site)) -> btw.reg
```

```{r}
btw.reg %>%
  filter(fb_shares < 500) %>%
  ggplot(aes(fb_shares, fill = site)) +
  geom_histogram(binwidth = 10)
```

```{r}
linreg <- lm(fb_shares ~ topic.f*site, data=btw.reg)

summary(linreg)
```

@@

{ 
  chart_topic_trends.dt %>%
  select(post_period, topic_name, articles) %>% 
  mutate(data_id = row_number() %>% as.character()) %>% 
  ggplot(aes(x = post_period, y = articles)) +
  geom_path_interactive(
    aes(group = topic_name, 
        tooltip = str_replace_all(topic_name, "'", ""),
        data_id = data_id), 
    color = "gray"
  ) +
    scale_y_continuous(labels = comma) +
    labs(
      title = "PEAKS AND TROUGHS",
      subtitle = "Hover over each line to see the trend of news articles for a particular topic",
      y = "Number of Articles"
    ) +
    theme(
      plot.background   = element_rect("#fafafa", "#fafafa"),
      plot.title        = element_text(size = 18),
      plot.subtitle     = element_text(size = 8),
      plot.caption      = element_text(size = 7),
      panel.grid        = element_blank(),
      panel.background  = element_rect("#fafafa"),
      axis.title.x      = element_blank(),
      axis.text.y       = element_text(size = 8)
    )
} %>% 
  ggiraph(
    ggobj = .,
    hover_css = "stroke: red; stroke-width: 3px;",
    width = 1,
    width_svg = 8,
    height_svg = 4,
    tooltip_extra_css = "
    font-family: Roboto; 
    background-color: #000; 
    color: #fff; font-size: 10px;
    padding: 5px;"
  ) %>% 
  prependContent(
    tags$link(
      href = "https://fonts.googleapis.com/css?family=Roboto:400,700", 
      rel = "stylesheet"
    )
  ) -> chart_trends_line.wdgt

@@

# Prepare dataset for joy plot
posts_classification.dt %>% 
  inner_join(
    btw2 %>% 
      mutate(document = as.numeric(articleID)) %>%
      select(
        document, 
        news_page = site, 
        title, 
        date
      ),
    by = "document"
  ) %>%
  inner_join(topics_mapping.dt, by = "topic") %>% 
  inner_join(
    btw2 %>% 
      mutate(document = as.numeric(articleID)) %>%
      group_by(document) %>%
      summarise(reactions = sum(fb_shares)) %>%
      ungroup(),
    by = "document"
  ) %>%
  group_by(
    topic_name, 
    # 8 hour time difference (Manila)
    week = floor_date(date, "week")
  ) %>% 
  summarise(
    num_articles  = sum(allocation),
    num_reactions = sum(reactions * allocation)
  ) %>%
  #mutate(peak = week[num_articles == max(num_articles)]) %>%
  ungroup() %>%
  arrange(week) %>%
  mutate(
    topic_name = factor(topic_name, levels = rev(unique(topic_name))),
    # ID needed for linking back information after tweening frames
    id = as.character(row_number()),
    # Maximum height for ridgeline is 9
    articles_height = num_articles/max(num_articles) * 9,
    reactions_height = num_reactions/max(num_reactions) * 9
  ) ->
  posts_time_trend.dt

@@

# Create animated pot
posts_time_trend.adt %>%
  ggplot(aes(x = week, y = topic_name, height = ht, 
             fill = topic_name, frame = .frame)) +
  geom_ridgeline(color = NA, alpha = 0.5) +
  geom_text(
    data = posts_time_trend_labels.adt,
    aes(x = min_week + 0.25 * range_week, 
        y = num_topics + 3.5, 
        alpha = 1 - opacity, 
        frame = .frame),
    label = "What news outlets publish", color = "forestgreen",
    family = "Roboto", fontface = "bold", size = 9,
    inherit.aes = FALSE
  ) +
  geom_text(
    data = posts_time_trend_labels.adt,
    aes(x = min_week + 0.75 * range_week, 
        y = num_topics + 3.5, 
        alpha = opacity, 
        frame = .frame),
    label = "What we react to", color = "firebrick",
    family = "Roboto", fontface = "bold", size = 9,
    inherit.aes = FALSE
  ) +
  geom_text(
    data = posts_time_trend_labels.adt,
    aes(x = min_week + 0.55 * range_week, 
        y = num_topics + 3.5, 
        frame = .frame),
    label = "VS",
    family = "Roboto", fontface = "bold", size = 7,
    inherit.aes = FALSE
  ) +
  scale_x_datetime(expand = c(0, 0)) +
  theme(
    legend.position = "none",
    panel.border    = element_blank(),
    axis.title      = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    plot.caption      = element_text(size = 9)
  ) + 
  labs(
    caption = "
DATA SOURCE: Webhose.io, Eventbride.com
CHART NOTE: Topics were derived through Latent Dirichlet Allocation (LDA) with 40 topics for online news articles in 2017 containing the term 'Bundestagswahl'
    "
  ) ->
  posts_time_trend.agg

@@

![Articles to Reactions](../figs/09-reactions-vs-articles.gif)

@@

set.seed(7292)
posts_classification.dt %>% 
  inner_join(
    btw2 %>% mutate(document = as.numeric(articleID)) %>%
      select(document, news_page = site, title),
    by = "document"
  ) %>%
  inner_join(topics_mapping.dt, by = "topic") %>% 
  group_by(news_page, topic_name) %>%
  summarise(
    articles = sum(allocation),
    sample_articles = 
      paste0(
        "<li>", sample(document, pmin(3, length(document))), "</li>",
        collapse = "<br>"
      )
  ) %>%
  ungroup() %>% 
  group_by(news_page) %>% 
  mutate(perc_articles = articles/sum(articles)) %>% 
  ungroup() %>%
  # left_join(
  #   top_100_fbpages.dt %>% select(news_page = page_name, page_title), 
  #   by = "news_page"
  # ) %>% 
  mutate(
    tooltip_text = 
      paste0(
        "<b>", comma(round(articles, 0)), " (", percent(perc_articles), 
        ") </b> of articles from <b>", news_page, 
        "</b> fall under <b>", topic_name, "</b><br><br>Sample Articles:<br><ul>",
        sample_articles, "</ul>"
      ) %>% str_replace_all("'", "")
  ) ->
  news_page_distribution.dt
```

>>>>

```{r}
suppressPackageStartupMessages({
  library(dplyr)       # Data manipulation
  library(stringr)     # String manipulation
  library(lubridate)   # Date and time manipulation
  library(purrr)       # Functional programming
  library(tidyr)       # Reshaping
  library(magrittr)    # Advanced piping
  library(pushoverr)   # Pushover notifications
  library(doMC)        # Parallel Computing
  library(readr)       # Importing data
  library(tibble)      # Better data frames
  library(data.table)

@@

rm(list=ls())
# Functions
source("func/topic-modelling-functions.R")
```

```{r caching, echo=, message=FALSE, warning=FALSE}
load("../output/btw_combined.Rda")
#load("../output/models/STM 25 .Rda")
```

### Tokenizing
```{r Tokenize}
btw %>% 
  unnest_tokens(word, text_cleaned, token = "words") %>%
  filter(str_length(word) >= 3) ->
  posts_tokenized.dt

# Structural Topic Model

## Preparation
### Build Corpus
```{r eval=FALSE, include=FALSE}
# Process data
processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("site","text_cleaned","month")],
                           wordLengths = c(2,Inf),
                           lowercase = F,
                           removestopwords = F,
                           removenumbers = F,
                           removepunctuation = F,
                           stem = F)
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
```

### Select number of topics
```{r}
K<-c(30,40,50,60)

t1 <- Sys.time()
kresult <- searchK(out$documents, 
                   out$vocab, 
                   K, 
                   prevalence=~site + s(month), 
                   data = out$meta,
                   max.em.its = 75,
                   seed =8458159,
                   init.type = "Spectral")
t2 <- Sys.time()
t2 - t1

save(btw, out, kresult, file="../output/models/kresult.Rda")
load(file="../output/models/kresult.Rda")
```

@@

## Run the Model
We then train the Structural Topic Model on the full dataset, with $k = 28$.

```{r}
k = 28 # Topics

@@

save(stmOut, btw, out, file=paste("../output/models/STM",k,".Rda"))
#load(file=paste("../output/models/STM",k,".Rda"))
```

@@

#### Extract posterior distributions
```{r Extract wtp and dtp}
# Word-topic probabilities
stmOut %>% tidy("beta") %>% filter(!is.na(topic)) -> posts.wtp

@@

#### Compute different word-relevance measures
```{r Compute relevance}
posts.wtp %>%
    filter(str_length(term) >= 3) %>%
  # Compute lambda and phi_kw
  mutate(lambda = 0.6, phi_kw = beta) %>% 
  # Compute and join the p_w
  left_join(
    posts_tokenized.dt %>%
      group_by(word) %>% 
      dplyr::summarise(frequency = sum(term_frequency)) %>% 
      ungroup() %>% 
      mutate(p_w = frequency/sum(frequency)) %>% 
      select(-frequency),
    by = c("term" = "word")
  ) %>%
  # Compute the relevance
  mutate(relevance = lambda * log(phi_kw) + (1 - lambda) * log(phi_kw/p_w)) ->
  word_relevance.dt
```

#### Topic Labeling
```{r Label Topics}
label <- labelTopics(stmOut, n=4)

prob <- as.data.frame(label$prob, stringsAsFactors = F)
frex <- as.data.frame(label$frex, stringsAsFactors = F)
lift <- as.data.frame(label$lift, stringsAsFactors = F)
score <- as.data.frame(label$score, stringsAsFactors = F)

topicLabel <- prob %>% 
  transmute(topic = rownames(.),
            topic_name = paste(prob$V1,prob$V2,prob$V3,score$V1,score$V2,score$V3, sep=","),
            prob = paste(prob$V1,prob$V2,prob$V3, sep=","),
            frex = paste(frex$V1,frex$V2,frex$V3, sep=","),
            lift = paste(lift$V1,lift$V2,lift$V3, sep=","),
            score = paste(score$V1,score$V2,score$V3, sep=","))

topicLabel$topic_name <- vapply(lapply(strsplit(topicLabel$topic_name, ","), unique), paste, character(1L), collapse = " ")
rm(prob, frex, lift, score)
```

```{r Add Topic to original DF}
# Create Dataframe
theta <- as.data.frame(stmOut$theta)
names(theta) <- as.character(1:25)
theta$topic <- colnames(theta)[apply(theta,1,which.max)]

doctopics.df <- theta %>%
  transmute(articleID = as.numeric(rownames(.)),
    topic = topic)

# Add Topic to origian DF
btw %>%
  inner_join(.,doctopics.df %>%
               mutate(topic=as.numeric(topic)), by="articleID") %>%
  ## Combine with Topic label
  left_join(., topicLabel %>%
              mutate(topic = as.numeric(topic)) %>%
              select(topic_name, topic) %>%
              mutate(topic = as.numeric(topic)), by="topic") -> btw

@@

@@

posts_classification.sdt <-
  posts.dtp %>% 
  group_by(articleID = document) %>% 
  summarise(topic = min(topic[gamma == max(gamma)]), gamma = max(gamma)) %>% 
  ungroup() %>%
  inner_join(btw %>% select(title, title_text, articleID, topic_name),
              by = "articleID") %>%
  #inner_join(topics_mapping.dt, by = "topic") %>%
  mutate(topic_title = 
           paste0("Topic ", formatC(topic, flag = "0", width = 2), 
                  " - ", topic_name)) %>%
  group_by(topic_name) %>% 
  top_n(300, gamma) %>%
  sample_n(10) %>% 
  mutate(row = row_number()) %>% 
  ungroup()

@@

ggsave(
  plot = {
    posts_classification.sdt %>% 
      ggplot(aes(x = 0, y = row, color = factor(topic, levels = 1:25))) +
      facet_wrap(~topic_title, ncol = 5) +
      geom_text(
        aes(label = title),
        size = 2, hjust = 0, family = "Roboto"
      ) +
      geom_point(aes(x = -0.025), size = 0.5) +
      scale_x_continuous(limits = c(-0.05, 1), expand = c(0, 0)) +
      scale_color_manual(
        values = rainbow(25) %>% 
          adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
      ) +
      theme(
        axis.title       = element_blank(),
        axis.text        = element_blank(),
        axis.ticks       = element_blank(),
        panel.grid       = element_blank(),
        strip.background = element_blank(),
        panel.border     = element_blank(),
        strip.text       = element_text(face = "bold", hjust = 0, size = 6),
        plot.background  = element_rect(fill = "#FAFAFA"),
        legend.position  = "none"
      ) 
  },
  device = "png",
  filename = "../figs/topic-classification-sample.png",
  dpi = 600, height = 10, width = 16
)

@@

### News landscape

@@

    ggsave(
      plot = {
        topic_labelling_top30words.dt %>% 
          ggplot(aes(x = x, y = y)) +
          geom_text_repel(
            aes(label = term, 
                color = factor(topic, levels = 1:25), 
                size = phi_kw * p_w), 
            lineheight = 0.6, 
            segment.size = NA,
            box.padding = unit(0, "lines"),
            force = 0.05,
            family = "Roboto"
          ) +
          geom_text_repel(
            data = topic_labelling_topics.dt,
            aes(label = str_wrap(topic_name, 15),
                color = factor(topic, levels = 1:25)),
            size = 2.25, lineheight = 0.7,
            segment.size = 0.5, alpha = 0.7,
            family = "Roboto", fontface = 2,
            force = 0.3
          ) +
          scale_size_continuous(range = c(1, 4)) +
          scale_color_manual(
            values = rainbow(25) %>% 
              adjustcolor(red.f = 0.6, green.f = 0.6, blue.f = 0.6)
          ) +
          theme(
            axis.title = element_blank(),
            axis.text  = element_blank(),
            axis.ticks = element_blank(),
            panel.grid = element_blank(),
            panel.border = element_blank(),
            plot.background = element_rect(fill = "#FAFAFA"),
            legend.position = "none"
          ) +
          labs(
            title    = ""
          )
      },
      filename = "../figs/news-landscape-map.png",
      device = "png",
      dpi = 600
    )

@@

@@

@@

{ 
  chart_topic_trends.dt %>%
  select(post_period, topic_name, articles) %>% 
  mutate(data_id = row_number() %>% as.character()) %>% 
  ggplot(aes(x = post_period, y = articles)) +
  geom_path_interactive(
    aes(group = topic_name, 
        tooltip = str_replace_all(topic_name, "'", ""),
        data_id = data_id), 
    color = "grey51"
  ) +
    scale_y_continuous(labels = comma) +
    labs(
      title = "PEAKS AND TROUGHS",
      subtitle = "Hover over each line to see the trend of news articles for a particular topic",
      y = "Number of Articles"
    ) +
    theme(
      plot.background   = element_rect("#fafafa", "#fafafa"),
      plot.title        = element_text(size = 18),
      plot.subtitle     = element_text(size = 8),
      plot.caption      = element_text(size = 7),
      panel.grid        = element_blank(),
      panel.background  = element_rect("#fafafa"),
      axis.title.x      = element_blank(),
      axis.text.y       = element_text(size = 8)
    )
} %>% 
  ggiraph(
    ggobj = .,
    hover_css = "stroke: hotpink; stroke-width: 3px;",
    width = 1,
    width_svg = 8,
    height_svg = 4,
    tooltip_extra_css = "
    font-family: Roboto; 
    background-color: #000; 
    color: #fff; font-size: 10px;
    padding: 5px;"
  ) %>% 
  prependContent(
    tags$link(
      href = "https://fonts.googleapis.com/css?family=Roboto:400,700", 
      rel = "stylesheet"
    )
  ) -> chart_trends_line.wdgt

@@

# Prepare dataset for joy plot
posts_classification.dt %>% 
  inner_join(
    btw %>% 
      mutate(document = as.numeric(articleID),
             date = as.POSIXct(date) ) %>%
      select(
        document, 
        news_page = site, 
        title, 
        date
      ),
    by = "document"
  ) %>%
  inner_join(topics_mapping.dt, by = "topic") %>% 
  inner_join(
    btw %>% 
      mutate(document = as.numeric(articleID)) %>%
      group_by(document) %>%
      summarise(reactions = sum(fb_shares)) %>%
      ungroup(),
    by = "document"
  ) %>%
  group_by(
    topic_name, 
    # 8 hour time difference (Manila)
    week = floor_date(date, "week")
  ) %>% 
  summarise(
    num_articles  = sum(allocation),
    num_reactions = sum(reactions * allocation)
  ) %>%
  #mutate(peak = week[num_articles == max(num_articles)]) %>%
  ungroup() %>%
  arrange(week) %>%
  mutate(
    topic_name = factor(topic_name, levels = rev(unique(topic_name))),
    # ID needed for linking back information after tweening frames
    id = as.character(row_number()),
    # Maximum height for ridgeline is 9
    articles_height = num_articles/max(num_articles) * 9,
    reactions_height = num_reactions/max(num_reactions) * 9
  ) ->
  posts_time_trend.dt

@@

# Create animated pot
posts_time_trend.adt %>%
  ggplot(aes(x = week, y = topic_name, height = ht, 
             fill = topic_name, frame = .frame)) +
  geom_ridgeline(color = NA, alpha = 0.5) +
  geom_text(
    data = posts_time_trend_labels.adt,
    aes(x = min_week + 0.25 * range_week, 
        y = num_topics + 3.5, 
        alpha = 1 - opacity, 
        frame = .frame),
    label = "What news outlets publish", color = "forestgreen",
    family = "Roboto", fontface = "bold", size = 9,
    inherit.aes = FALSE
  ) +
  geom_text(
    data = posts_time_trend_labels.adt,
    aes(x = min_week + 0.75 * range_week, 
        y = num_topics + 3.5, 
        alpha = opacity, 
        frame = .frame),
    label = "What we react to", color = "firebrick",
    family = "Roboto", fontface = "bold", size = 9,
    inherit.aes = FALSE
  ) +
  geom_text(
    data = posts_time_trend_labels.adt,
    aes(x = min_week + 0.55 * range_week, 
        y = num_topics + 3.5, 
        frame = .frame),
    label = "VS",
    family = "Roboto", fontface = "bold", size = 7,
    inherit.aes = FALSE
  ) +
  scale_x_datetime(expand = c(0, 0)) +
  theme(
    legend.position = "none",
    panel.border    = element_blank(),
    axis.title      = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    plot.caption      = element_text(size = 9)
  ) + 
  labs(
    caption = ""
  ) ->
  posts_time_trend.agg

@@

#![Articles to Reactions](../figs/09-reactions-vs-articles.gif)

@@

set.seed(7292)
posts_classification.dt %>% 
  inner_join(
    btw %>% mutate(document = as.numeric(articleID)) %>%
      select(document, news_page = site, title),
    by = "document"
  ) %>%
  inner_join(topics_mapping.dt, by = "topic") %>% 
  group_by(news_page, topic_name) %>%
  summarise(
    articles = sum(allocation),
    sample_articles = 
      paste0(
        "<li>", sample(document, pmin(3, length(document))), "</li>",
        collapse = "<br>"
      )
  ) %>%
  ungroup() %>% 
  group_by(news_page) %>% 
  mutate(perc_articles = articles/sum(articles)) %>% 
  ungroup() %>%
  # left_join(
  #   top_100_fbpages.dt %>% select(news_page = page_name, page_title), 
  #   by = "news_page"
  # ) %>% 
  mutate(
    tooltip_text = 
      paste0(
        "<b>", comma(round(articles, 0)), " (", percent(perc_articles), 
        ") </b> of articles from <b>", news_page, 
        "</b> fall under <b>", topic_name, "</b><br><br>Sample Articles:<br><ul>",
        sample_articles, "</ul>"
      ) %>% str_replace_all("'", "")
  ) ->
  news_page_distribution.dt
```
